Trifunctional Phosphatidylethanolamine

### 2025-02-24 IndividualStudies/AT_2025.qmd
Added documentation to MaintenanceInstructions, improved standardization

AT_2025 <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/AT_ChemicalCommunications_2025_download.csv"))

# Organize the hit annotations as factors
AT_2025$hit_annotation <- factor(pull(AT_2025, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)

# Building an ID column to maintain the order on the x-axis
ID <- c()
for(i in 0:(nrow(AT_2025)/2)){
	ID[i] = i
}

# Applies the ID column to the PE results
AT_2025_ranked_PE <- AT_2025 |>
    arrange(logFC) |>
	filter(LipidProbe == "PE") |>
	mutate(ID = ID)

# Applies the ID column to the PA results
AT_2025_ranked_PA <- AT_2025 |>
    arrange(logFC) |>
	filter(LipidProbe == "PA") |>
	mutate(ID = ID)

# Assembles the dataset to plot
AT_2025_ranked <- rbind(AT_2025_ranked_PE, AT_2025_ranked_PA)

@@

VolcanoPlotStandardized(AT_2025)

@@

RankedOrderPlotStandard(AT_2025_ranked)
```
:::

@@

## Creates a reactive dataframe
AT_2025_reactive <- crosstalk::SharedData$new(AT_2025)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = AT_2025_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = AT_2025_reactive,
                  group = ~hit_annotation)
)

@@

## Displays the reactive dataframe
datatable(AT_2025_reactive, options = list(pageLength = 20))

>>>>

data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/AT_ChemicalCommunications_2025_download.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)

@@

VolcanoPlotStandardized(data)

@@

RankedOrderPlotStandard(data)
```
:::

@@

## Creates a reactive dataframe
data_reactive <- crosstalk::SharedData$new(data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation)
)

@@

## Displays the reactive dataframe
datatable(data_reactive, options = list(pageLength = 20))

### 2025-02-24 IndividualStudies/SF_2024.qmd
Added documentation to MaintenanceInstructions, improved standardization

# Opening the datatable for this page IN FINAL RENDER
SF_2024_data <- readr::read_csv("DataTables/SF_ACS-Chem-Bio_2024_download.csv")

# # # Opening the datatable for this page WHILE EDITING
# SF_2024_data <- readr::read_csv("IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv")

# Organize the hit annotations as factors
SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

# Organize the probes as factors
SF_2024_data$LipidProbe <- factor(pull(SF_2024_data, LipidProbe), levels = c("Sph", "Spa", "8-3 FA", "1-10 FA"), ordered = TRUE)

# Building an ID column to maintain the order on the x-axis
ID <- c()
for(i in 0:(nrow(SF_2024_data)/2)){
	ID[i] = i
}

# Applies the ID column to the Spa results
SF_2024_ranked_Spa <- SF_2024_data |>
    arrange(logFC) |>
	filter(LipidProbe == "Spa") |>
	mutate(ID = ID)

# Applies the ID column to the Sph results
SF_2024_ranked_Sph <- SF_2024_data |>
    arrange(logFC) |>
	filter(LipidProbe == "Sph") |>
	mutate(ID = ID)

# Assembles the dataset to plot
SF_2024_ranked <- rbind(SF_2024_ranked_Sph, SF_2024_ranked_Spa)
```

@@

VolcanoPlotStandardized(SF_2024_data)

@@

RankedOrderPlotStandard(SF_2024_ranked)
```
:::

@@

MAStandard(SF_2024_data)

@@

@@

@@

SF_2024_data <- SF_2024_data |>
  select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe)

## Creates a reactive dataframe
SF_2024_data_reactive <- crosstalk::SharedData$new(SF_2024_data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = SF_2024_data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = SF_2024_data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(SF_2024_data_reactive, 
          options = list(pageLength = 15),
                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))

>>>>

# Opening the datatable for this page IN FINAL RENDER
data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv"))

# # # Opening the datatable for this page WHILE EDITING
# data <- readr::read_csv("IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv")

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

# Organize the probes as factors
data$LipidProbe <- factor(pull(data, LipidProbe), levels = c("Sph", "Spa", "8-3 FA", "1-10 FA"), ordered = TRUE)

@@

VolcanoPlotStandardized(data)

@@

RankedOrderPlotStandard(data)
```
:::

@@

MAStandard(data)

@@

:::
:::

## Gene Ontology enrichment

**In beta: GO analysis still under development**

#### Cell Compartment

:::{.border}

<iframe src="/IndividualStudies/GO_plots/Sph-Spa_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>

![](/IndividualStudies/GO_plots/Sph-Spa_SF_2024_CC-CNETplot.png)

@@

#### Molecular Function

:::{.border}

<iframe src="/IndividualStudies/GO_plots/Sph-Spa_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>

(MF CNET plot failed in production)
:::

#### Biological Process

:::{.border}

(No BP pathways identified among enriched hits and candidates.)

(BP CNET plot failed in production)
:::

@@

data <- data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe)

## Creates a reactive dataframe
data_reactive <- crosstalk::SharedData$new(data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 15),
                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))

### 2025-02-24 IndividualStudies/SF_2024_B.qmd
Added documentation to MaintenanceInstructions, improved standardization

# Opening the datatable for this page IN FINAL RENDER
SF_2024_data <- readr::read_csv("DataTables/SF_Chem_Comm_2024_download.csv")

# # # Opening the datatable for this page WHILE EDITING
# SF_2024_data <- readr::read_csv("IndividualStudies/DataTables/SF_Chem_Comm_2024_download.csv")

# Organizing the hit annotations as factors
SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

# Organize the probes as factors
SF_2024_data$LipidProbe <- factor(pull(SF_2024_data, LipidProbe), levels = c("Spa", "Sph", "8-3 FA", "1-10 FA"), ordered = TRUE)

#write.csv(SF_2024_data, "IndividualStudies/DataTables/SF_Chem_Comm_2024_download.csv")

# Building an ID column to maintain the order on the x-axis
ID <- c()
for(i in 0:(nrow(SF_2024_data)/2)){
	ID[i] = i
}

# Applies the ID column to the 1-10 FA results
SF_2024_ranked_1_10_FA <- SF_2024_data |>
    arrange(logFC) |>
	filter(LipidProbe == "1-10 FA") |>
	mutate(ID = ID)

# Applies the ID column to the 8-3 FA results
SF_2024_ranked_8_3_FA <- SF_2024_data |>
    arrange(logFC) |>
	filter(LipidProbe == "8-3 FA") |>
	mutate(ID = ID)

# Assembles the dataset to plot
SF_2024_ranked <- rbind(SF_2024_ranked_8_3_FA, SF_2024_ranked_1_10_FA)
```

@@

## Study details

#### Authors
Scotland E. Farley, Ryu Hashimoto, Judah Evangelista, Frank Stein, Per Haberkant, Kazuya Kikuchi, Fikadu G. Tafesse, Carsten Schultz

#### Journal
Chemical Communications

<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}

#### Abstract

Functionalized lipid probes are a critical new tool to interrogate the function of individual lipid species, but the structural parameters that constrain their utility have not been thoroughly described. Functionalized lipid probes are a critical new tool to interrogate the function of individual lipid species, but the structural parameters that constrain their utility have not been thoroughly described. Here, we synthesize three palmitic acid derivatives with a diazirine at different positions on the acyl chain and examine their metabolism, subcellular localization, and protein interactions. We demonstrate that while they produce very similar metabolites and subcellular distributions, probes with the diazirine at either end pulldown distinct subsets of proteins after photo-crosslinking. This highlights the importance of thoughtful diazirine placement when developing probes based on biological molecules.

#### Lipid probes utilized

[8-3 Fatty Acid](/LipidProbe/8-3_FattyAcid.qmd)

#### Cell line analyzed

[Huh7](https://huh7.com){target="_blank"}

#### Mass spectrometry quantification method

16-channel Tandem Mass Tagging (TMT16)

#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
:::

@@

## Enriched Proteins

@@

SF_2024_data <- SF_2024_data |>
  select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe)

## Creates a reactive dataframe
SF_2024_data_reactive <- crosstalk::SharedData$new(SF_2024_data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = SF_2024_data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = SF_2024_data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(SF_2024_data_reactive, options = list(pageLength = 15))

>>>>

# Opening the datatable for this page IN FINAL RENDER
data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_Chem_Comm_2024_download.csv"))

# Organizing the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

# Organize the probes as factors
data$LipidProbe <- factor(pull(data, LipidProbe), levels = c("Spa", "Sph", "8-3 FA", "1-10 FA"), ordered = TRUE)

@@

{{< include /StudyInformation_includes/SF_2024_B_include.qmd >}}

:::

@@

## Gene Ontology enrichment

**In beta: GO analysis still under development**

#### Cell Compartment

:::{.border}

<iframe src="/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>

![](/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-CNETplot.png)

:::

#### Molecular Function

:::{.border}

<iframe src="/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>

(MF CNET plot failed in production)
:::

#### Biological Process

:::{.border}

<iframe src="/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_BP-DOTplot.html" width="100%" height="500px"></iframe>

(BP CNET plot failed in production)
:::

:::

## Data exploration and download

@@

data <- data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe)

## Creates a reactive dataframe
data_reactive <- crosstalk::SharedData$new(data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(data_reactive, options = list(pageLength = 15))

### 2025-02-24 LipidProbe/1-10_FattyAcid.qmd
Added documentation to MaintenanceInstructions, improved standardization

---
title: "Trifunctional 1-10 Fatty Acid"
crossref: 
  ref-hyperlink: true # (default is true)
prefer-html: true
html: default
---

@@

# SF_2024_data <- readr::read_csv("LipidProbe/DataSets/SF_Chem_Comm_2024_download.csv") |>
# 	filter(LipidProbe == "1-10 FA")

# write.csv(SF_2024_data, "LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv")

# Opening the datatable for this page
SF_2024_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv")) |>
	filter(LipidProbe == "1-10 FA")

# Organizing the hit annotations as factors
SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

# Building an ID column to maintain the order on the x-axis
ID <- c()
for(i in 0:(nrow(SF_2024_data))){
	ID[i] = i
}

# Applies the ID column to the Spa results
SF_2024_ranked <- SF_2024_data |>
    arrange(logFC) |>
	filter(LipidProbe == "1-10 FA") |>
	mutate(ID = ID)

@@

VolcanoPlotStandardized(SF_2024_data)
```
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
# #### These functions make the plots to be displayed in this div - uncomment them to run them again
# CC_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/1-10FA_SF_2024_CC-DOTplot")
# CC_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/1-10FA_SF_2024_CC-CNETplot")
```

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# MF_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/1-10FA_SF_2024_MF-DOTplot")
# MF_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/1-10FA_SF_2024_MF-CNETplot")
```

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# BP_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/1-10FA_SF_2024_BP-DOTplot")
# BP_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/1-10FA_SF_2024_BP-CNETplot")
```

@@

SF_2024_data <- SF_2024_data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe)

## Creates a reactive dataframe
SF_2024_data_reactive <- crosstalk::SharedData$new(SF_2024_data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = SF_2024_data_reactive,
                  group = ~hit_annotation,
									inline=TRUE)
)

## Displays the reactive dataframe
datatable(SF_2024_data_reactive, 
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10),
                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))

@@

{{< downloadthis DataSets/1-10_FA_Huh7_SF_2024.csv dname="1-10_FA_Huh7_SF_ACS-Chem-Bio_2024.csv">}}

>>>>

---
title: "Trifunctional 1-10 Fatty Acid"
crossref: 
  ref-hyperlink: true # (default is true)
prefer-html: true
---

@@

# Opening the datatable for this page
data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv")) |>
	filter(LipidProbe == "1-10 FA")

# Organizing the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

@@

VolcanoPlotStandardized(data)
```
:::

@@

:::{.border}

@@

:::{.border}

@@

:::{.border}

@@

data <- data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
          fdr = signif(fdr, digits = 3)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe)

## Creates a reactive dataframe
data_reactive <- crosstalk::SharedData$new(data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation,
									inline=TRUE)
)

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10),
                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))

@@

{{< downloadthis DataSets/1-10_FA_Huh7_SF_2024.csv dname="1-10_FA_Huh7_SF_ACS-Chem-Bio_2024">}}

### 2025-02-24 LipidProbe/8-3_FattyAcid.qmd
Added documentation to MaintenanceInstructions, improved standardization

# SF_2024_data <- readr::read_csv("LipidProbe/DataSets/SF_Chem_Comm_2024_download.csv") |>
# 	filter(LipidProbe == "8-3 FA")

# write.csv(SF_2024_data, "LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv")

# Opening the datatable for this page
SF_2024_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv")) |>
	filter(LipidProbe == "8-3 FA")

# Organizing the hit annotations as factors
SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

# Building an ID column to maintain the order on the x-axis
ID <- c()
for(i in 0:(nrow(SF_2024_data))){
	ID[i] = i
}

# Applies the ID column to the Spa results
SF_2024_ranked <- SF_2024_data |>
    arrange(logFC) |>
	filter(LipidProbe == "8-3 FA") |>
	mutate(ID = ID)

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
# #### These functions make the plots to be displayed in this div - uncomment them to run them again
# CC_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/8-3FA_SF_2024_CC-DOTplot")
# CC_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/8-3FA_SF_2024_CC-CNETplot")
```

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# MF_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/8-3FA_SF_2024_MF-DOTplot")
# MF_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/8-3FA_SF_2024_MF-CNETplot")
```

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#### These functions make the plots to be displayed in this div - uncomment them to run them again
# BP_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/8-3FA_SF_2024_BP-DOTplot")
# BP_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/8-3FA_SF_2024_BP-CNETplot")
```

@@

{{< downloadthis DataSets/8-3_FA_Huh7_SF_2024.csv dname="8-3_FA_Huh7_SF_ACS-Chem-Bio_2024.csv">}}

>>>>

# Opening the datatable for this page
data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv")) |>
	filter(LipidProbe == "8-3 FA")

# Organizing the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

@@

:::{.border}

@@

:::{.border}

@@

:::{.border}

@@

{{< downloadthis DataSets/8-3_FA_Huh7_SF_2024.csv dname="8-3_FA_Huh7_SF_ACS-Chem-Bio_2024">}}

### 2025-02-24 LipidProbe/PhosphatidicAcid.qmd
Added documentation to MaintenanceInstructions, improved standardization

---
title: "Trifunctional Phosphatidic Acid"
---

@@

# AT_2025_Long <- readr::read_csv("LipidProbe/DataSets/AT_ChemicalCommunications_2025_download.csv") |>
# 	filter(LipidProbe == "PA")

# write.csv(AT_2025_Long, "LipidProbe/DataSets/PA_HeLa_AT_2025.csv")

AT_2025_Long <- readr::read_csv("DataSets/PA_HeLa_AT_2025.csv")

# Organize the hit annotations as factors
AT_2025_Long$hit_annotation <- factor(pull(AT_2025_Long, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)

# Building an ID column to maintain the order on the x-axis
ID <- c()
for(i in 0:(nrow(AT_2025_Long))){
	ID[i] = i
}

# Applies the ID column to the PE results
AT_2025_ranked <- AT_2025_Long |>
    arrange(logFC) |>
	filter(LipidProbe == "PA") |>
	mutate(ID = ID)

@@

VolcanoPlotStandardized(AT_2025_Long)

@@

##### Data

@@

AT_2025_Long <- AT_2025_Long |>
  select(gene_name, hit_annotation, logFC, pvalue) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(hit_annotation)

## Creates a reactive dataframe
AT_2025_Long_reactive <- crosstalk::SharedData$new(AT_2025_Long)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = AT_2025_Long_reactive,
                  group = ~hit_annotation,
                  inline="true")
)

## Displays the reactive dataframe
datatable(AT_2025_Long_reactive,
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10))

@@

{{< downloadthis DataSets/PA_HeLa_AT_2025.csv dname="PA_HeLa_AT_ChemComm_download.csv">}}

>>>>

---
title: "Trifunctional Phosphatidic Acid"
prefer-html: true
format:
  html: default

---

@@

# AT_2025 <- readr::read_csv("LipidProbe/DataSets/AT_ChemicalCommunications_2025_download.csv") |>
# 	filter(LipidProbe == "PA")

# write.csv(AT_2025, "LipidProbe/DataSets/PA_HeLa_AT_2025.csv")

data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)

@@

VolcanoPlotStandardized(data)

@@

:::
:::

## Gene Ontology enrichment

**In beta: GO analysis still under development**

#### Cell Compartment

:::{.border}

<iframe src="/LipidProbe/GO_plots/PA_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>

(CC CNET plot failed in production)
:::

#### Molecular Function

:::{.border}

<iframe src="/LipidProbe/GO_plots/PA_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>

(MF CNET plot failed in production)
:::

#### Biological Process

:::{.border}

<iframe src="/LipidProbe/GO_plots/PA_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>

(BP CNET plot failed in production)
:::
:::

## Data exploration and download

@@

data <- data |>
  dplyr::select(gene_name, hit_annotation, logFC, pvalue) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(hit_annotation)

## Creates a reactive dataframe
data_reactive <- crosstalk::SharedData$new(data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation,
                  inline="true")
)

## Displays the reactive dataframe
datatable(data_reactive,
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10))

@@

{{< downloadthis DataSets/PA_HeLa_AT_2025.csv dname="PA_HeLa_AT_ChemComm_download">}}

### 2025-02-24 LipidProbe/Phosphatidylethanolamine.qmd
Added documentation to MaintenanceInstructions, improved standardization

---
title: "Trifunctional Phosphatidylethanolamine"
---

@@

# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
# Read the data to a df

# AT_2025_Long <- readr::read_csv("LipidProbe/DataSets/AT_ChemicalCommunications_2025_download.csv") |>
# 	filter(LipidProbe == "PE")

# write.csv(AT_2025_Long, "LipidProbe/DataSets/PE_HeLa_AT_2025.csv")

AT_2025_Long <- readr::read_csv("DataSets/PE_HeLa_AT_2025.csv")

# Organize the hit annotations as factors
AT_2025_Long$hit_annotation <- factor(pull(AT_2025_Long, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)

# Building an ID column to maintain the order on the x-axis
ID <- c()
for(i in 0:(nrow(AT_2025_Long))){
	ID[i] = i
}

# Applies the ID column to the PE results
AT_2025_ranked <- AT_2025_Long |>
    arrange(logFC) |>
	filter(LipidProbe == "PE") |>
	mutate(ID = ID)

@@

##### Data

@@

AT_2025_Long <- AT_2025_Long |>
  select(gene_name, hit_annotation, logFC, pvalue) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(hit_annotation)

## Creates a reactive dataframe
AT_2025_Long_reactive <- crosstalk::SharedData$new(AT_2025_Long)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = AT_2025_Long_reactive,
                  group = ~hit_annotation,
                  inline="true")
)

@@

## Displays the reactive dataframe
datatable(AT_2025_Long_reactive,
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10))
```
:::

{{< downloadthis DataSets/PE_HeLa_AT_2025.csv dname="PE_HeLa_AT_ChemComm_download.csv">}}

>>>>

---
title: "Trifunctional Phosphatidylethanolamine"
prefer-html: true
format:
  html: default

---

@@

# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.

# Read the data to a df
data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/PE_HeLa_AT_2025.csv"))

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)

# Building an ID column to maintain the order on the x-axis
ID <- c()
for(i in 0:(nrow(data))){
	ID[i] = i
}

# Applies the ID column to the PE results
AT_2025_ranked <- data |>
    arrange(logFC) |>
	filter(LipidProbe == "PE") |>
	mutate(ID = ID)

@@

```
:::
:::

## Gene Ontology enrichment

**In beta: GO analysis still under development**

#### Cell Compartment

:::{.border}

<iframe src="/LipidProbe/GO_plots/PE_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>

(CC CNET plot failed in production)
:::

#### Molecular Function

:::{.border}

<iframe src="/LipidProbe/GO_plots/PE_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>

(MF CNET plot failed in production)
:::

#### Biological Process

:::{.border}

<iframe src="/LipidProbe/GO_plots/PE_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>

(BP CNET plot failed in production)
:::
:::

## Data exploration and download

@@

data <- data |>
  dplyr::select(gene_name, hit_annotation, logFC, pvalue) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(hit_annotation)

## Creates a reactive dataframe
data_reactive <- crosstalk::SharedData$new(data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation,
                  inline="true")
)

@@

## Displays the reactive dataframe
datatable(data_reactive,
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10))
```
:::

{{< downloadthis DataSets/PE_HeLa_AT_2025.csv dname="PE_HeLa_AT_ChemComm_download">}}
